Cognitive Priming: Impact on the Perception of a Robot

### 2015-10-29 main.tex
Cognitive context -> Cognitive priming (may be incomplete)

\rightheader{Cognitive Context: Impact on the Perception of a Robot}   % This should be the title, or a shortened version of the title if your title is long.
\leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
\title{Cognitive Context: Impact on the Perception of a Robot}

@@

\keywords{human-robot interaction, anthropomorphism, cognitive context, eye-tracking, gaze patterns}

@@

Robotics researchers often tend to consider that anthropomorphism only describes
a static set of human-like features of a robot (like its shape, its speech
capabilities, facial expressions, etc.).
Following~\citet{fink_anthropomorphism_2012}, we refer to these characteristics
as the \emph{anthropomorphic design} of the robot, and we call
\emph{anthropomorphism} the general \emph{social phenomenon} that emerges from
the (real or imagined) interaction between a non-human agent (a robot in our
case) and a human~\citep{persson_anthropomorphism_2000}.  According
to~\citet{epley_when_2008}, anthropomorphism includes the human perception of
emotional states, motivations, intentions in the non-human agent, and tends to
ascribe those qualities to it. As such, the dynamic and socio-cognitive
dimensions of anthropomorphism are essential to understand the complex bonds
that human users build with artificial agents such as
robots~\citep{lemaignan2014dynamics}. Therefore anthropomorphism appears to be a
useful \emph{proxy} to study these intricate psychological
bonds. Going in that direction, this article introduces new ways to assess
anthropomorphic attributions and provides in particular new insights on
the impact of the cognitive context of the interaction on anthropomorphic
attributions.

@@

We actually build several hypotheses: our baseline hypothesis \h{1} is that we
can actually create such stimuli that induce recognisable \emph{shallow
cognitive contexts} and \emph{deep cognitive contexts} (manipulation check); and
further that these contexts are interpreted by the participants as being
respectively \emph{machine-like} (low level of anthropomorphic attributions) or
\emph{human-like} (higher level of anthropomorphic attributions).

@@

Then, we hypothesize (\h{3}) that the gaze fixations on the head are
significantly different depending on the cognitive context, and that a deeper
cognitive context corresponds to longer gaze fixations on the head. This would
in turn interpreted at \emph{gaze fixations on the head is a proxy for the level
of human-likeness attribution}, and constitutes the core hypothesis of this
article.

Finally, the hypothesis \h{4} examines whether the cognitive context affects the
general tendency to anthropomorphize, \ie whether observing \emph{one}
robot acting in an \emph{human-like} context leads to an increased level of
anthropomorphic attributions to robots \emph{in general}. This also provides us
with a way to triangulate the behavioural measures with the subjective
attribution of anthropomorphism: if such an effect is found, we can also
conclude that the cognitive context impacts on the attribution of human-likeness,
and this, in turns, supports the hypothesis \h{3} that head fixations would
reflect not only the cognitive context but also the level of anthropomorphic
attributions.

Figure~\ref{hyps} illustrate how these four hypotheses relate to \emph{a)}
cognitive context, \emph{b)} anthropomorphic attributions, and \emph{c)} gaze
patterns.

@@

    \node at (0,0) (ctxt) {Cognitive context};
    \node at (-3,-3) (anthro) {Anthropomorphic attributions};
    \node at (3,-3)[circle split, text width=2.5cm] (gaze) {\textit{\small Fixations \\on head} \nodepart{lower} \textit{\small Gaze
distribution \\differences}};
    \node [draw=none,anchor=east,left=-0.5cm of gaze.west] (gazecap) {\large Gaze:};

@@

\pagebreak
\section{Experimental Design}

As hinted, this study is build as an eye-tracking experiment (using a stationary
eye-tracker SMI RED 250) where participants watch short videos of an agent --
either a robot (Aldebaran Robotics' Nao) or a human -- performing very simple
task (picking an object or pointing toward a sound source), in two different
socio-cognitive contexts.  These contexts, created by priming and/or audio cues,
are designed to elicit either a shallow cognitive context (that participants
would \textit{a posteriori} rate as a \emph{machine-like situation}) or a deeper
cognitive context (rated as a \emph{human-like situation}).

@@

The study follows a 2$\times$2 design, summarized in table~\ref{table:design}. Our two
independent variables are the level of socio-cognitive context (\emph{shallow
cognitive context} \vs \emph{deep cognitive context}) and the nature of the
agent appearing in the stimulus (a robot, eliciting a \emph{human-robot} interaction
situation, or a human, eliciting a \emph{human-human} interaction
situation).

@@

    \tikzmark{left}
    \begin{tabular}{l|p{4cm}|p{4cm}}
        & \tikzmark{top1} Shallow cognitive context & Deep cognitive context \tikzmark{top2}  \\
        \hline
        \tikzmark{left1} Robot & {\bf A}: \emph{``Pick the brown toy''} & {\bf A}: \emph{``Pick your favorite toy''} \\
                               & {\bf B}: \emph{``Point at the noise''} & {\bf B}: \emph{``Point at the crying baby''} \\
        \hline
        \tikzmark{left2} Human & {\bf A}: \emph{``Pick the brown toy''} & {\bf A}: \emph{``Pick your favorite toy''} \\ 
                               & {\bf B}: \emph{``Point at the noise''} & {\bf B}: \emph{``Point at the crying baby''}\tikzmark{bottom} \\
        \end{tabular}

@@

    \caption{\small The study follows a 2$\times$2 design: the \emph{robot} vs
        \emph{human} condition is within subject, while the \emph{shallow
        cognitive context} \vs \emph{deep cognitive context} is between subjects.
        Two stimuli (\emph{Picking} task, {\bf A}, and \emph{Pointing} task,
        {\bf B}) were shown to the participants, introduced by brief verbal
        commands, reproduced in the table. Figure~\ref{fig:stimuli} shows
        pictures of the four stimuli.}

@@

The audio (and audio only) of these four videos was then edited to create two
sets of stimuli: one for the \emph{shallow cognitive context} condition, one for
the \emph{deep cognitive context} condition. The audio editing consisted in
inserting different commands to initiate the tasks (reported in
table~\ref{table:design}): in the \emph{Picking} task for instance, the object
that the agent had to pick was described either as a \emph{``brown toy''} or as
\emph{``your favorite toy''}. In the former case, the object was refered through
visible, objective features which do not suppose as deep cognitive capabilities
as in the latter case where the agent is implicitly supposed to have
tastes and preferences such as it can choose a toy as its favorite.

This simple verbal priming (\emph{``brown toy''} \vs \emph{``your favorite
toy''}) set the cognitive context (\emph{shallow} \vs \emph{deep}) and was
expected to lead to different perceptions of the interaction
(\emph{machine-like} \vs \emph{human-like}). We reinforced this effect in the
\emph{Pointing} task: not only the verbal priming but also the sound played by the
speakers during the task was altered: either a repetitive bip (\emph{shallow
cognitive context}) or the sound of a crying baby (\emph{deeper cognitive
context}).

@@

\pagebreak
\section{Method}

@@

As stated previously, the study follows a 2$\times$2 design
(table~\ref{table:design}): the \emph{deep} \vs \emph{shallow cognitive context}
condition was between-subjects (30 participants performed the \emph{deep cognitive}
tasks while 26 were in the \emph{shallow cognitive} condition); the \emph{robot}
\vs \emph{human} condition was within-subject (the order of stimuli presentation
was counter-balanced over the participants). The study lasted in average 15
minutes per participant.

@@

\pagebreak
\section{Results}

Based on the experiments conducted on 56 participants in the human and robot
interactions across \emph{shallow} and \emph{deep cognitive context} conditions,
we have the following results.\footnote{The detailed statistics and code used
    for obtaining the results are available here :
\url{https://github.com/chili-epfl/anthropomorphism-eyetracking}.}

@@

Participants were asked in the post-questionnaire whether the video presented a
\emph{``robot kind of task''} or a \emph{``human kind of task''} on a 5-points
scale (numerical values ranging from -2 to 2, where -2 refers to robot kind of
task). As can be seen in figure 2, we got a significant correlation in this
manipulation check ($F(1,54) = 29.0, p < .001$) which validates our manipulation
and supports \h{1}: the participants that were shown the \emph{shallow cognitive
context} videos identified the task as more robot-like and participants watching
\emph{deep cognitive context} videos perceived the tasks as more human-like.

@@

\subsection{Gaze Behaviours in Shallow \vs Deep Cognitive Contexts}

We consider the 5 groups of AOIs {\sf head}, {\sf arms}, {\sf hands}, {\sf
torso} and {\sf legs} (the left and right arms, hands and legs are grouped
together). Based on ANOVA results for the robot in both the shallow and deep
cognitive context conditions, the fixations on the head in the deep condition
were found to be significantly higher than that in the shallow condition
($F(1,54) = 4.2, p < .05$\fixme{put the exact p value here}). For all other AOIs groups, the fixations across
shallow and deep conditions were almost the same. Figure~\ref{h3} shows the
distribution of proportion of time spent gazing on the 5 AOI groups for the two
conditions.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.6\columnwidth]{GazeHighLow}\label{GazeHighLow}
    \caption{Gaze fixations on the different areas on interest, for shallow \vs
    deep cognitive context conditions.}
    \label{h3}
\end{figure}

@@

Note that we only analysed these possible correlations for robot condition: in
the human condition, the presence of the human is intrinsically a source of deep
cognitive context, hiding the effects of our manipulation on a shallow \vs deep
cognitive context.

\subsection{Correlation Between Cognitive Context and Changes in Anthropomorphic
Attributions}

Running an ANOVA against the change of anthropomorphic attributions
(\deltaant) over the duration of the experiment in the two cognitive
conditions, shows that \deltaant is greater for tasks with a deeper cognitive
context than that for the shallow cognitive tasks ($F(1,54) = 6.54, p <
.05$\fixme{put the exact p value here},
figure~\ref{h4}). In other words, after being exposed to short videos of a robot
performing simple tasks, participants primed with a deeper cognitive context report
a significantly higher tendency to anthropomorphize robots \emph{in general} (as
the questionnaire on anthropomorphic attributions explicitly referred to
\emph{robots in general}).

\begin{figure}
    \centering
    \includegraphics[width=3.3in]{H4}\label{ICAtoAAPImprovement}
    \caption{Difference between \anti{} and \antf{} in the shallow and deep
    cognitive contexts.}
    \label{h4}
\end{figure}

This result supports \h{4} and validate that the cognitive context impacts the
attribution of anthropomorphic features to robots. This, in turn, supports the
\emph{proxy} hypothesis of \h{3}: \emph{head fixations are a proxy for higher
levels of human-likeness attributions}.

@@

\pagebreak
\section{Discussion and Conclusion}

@@

The significant correlation between deep \vs shallow conditions and the
answers to the question \emph{Were the task more robot-like or human-like?}
shows that our manipulation was successful, and that a shallow cognitive
context was indeed associated to a robot-like situation, while a deeper
cognitive context was associated to a human-like situation (\h{1}). This is
already an interesting result: subtle changes in the cognitive contexts are
recognized and clearly interpreted in terms of human-likeness.

@@

The third hypothesis \h{3} proposes that head fixations are related to the
cognitive context, which is clearly supported by our data: in deeper cognitive
context, one tends to spend more time looking at the head of the interacting
agent than in a shallow cognitive context. We also hypothesized that, in turn,
head fixations could act as a \emph{proxy to anthropomorphic projections}: as
underlined in the previous section, our data also support this.

Finally, the hypothesis \h{4} looks at the dynamic of anthropomorphic
projections, with the hypothesis that watching an interaction with a particular
robot in a deeper cognitive context may impact \emph{globally} the
anthropomorphic perceptions of robots. This is supported by our study.

\subsection{Summary and Contributions}

The study and results presented in this article lead to two main contributions:
new insights on the impact of the cognitive context on the perception of a robot
by humans; a novel unbiased methodology based on eye-tracking to assess
anthropomorphic attributions during a running human-robot interaction.

This leads to a second-order effect that we also evidence here: depending on the
cognitive context, the tendency to attribute human-like characteristics to robot
evolves in significantly different ways. After observing a robot in a
context that pre-suppose deeper cognitive capabilities, people increase
their general tendency to anthropomorphize robots compared to a shallow
cognitive context, even though the robot appearance and visual behaviour is the
exact same.

@@

Finally, the situations needed to support two possible cognitive contexts
(shallow \vs deeper cognitive context), and triggering one or the other of these
contexts needed to be done \emph{without changing} the visual part of the
stimulus.

We initially prepared three different stimuli: the \emph{Picking} task, the
\emph{Pointing} task and a \emph{Dance} task.  During the \emph{Dance} task, the
agent was either asked to \emph{``Show some movements''} (\emph{shallow
cognitive context} condition) or to \emph{``Dance with the music''}
(\emph{deeper cognitive context} condition). While all the participants were
shown this stimuli as well, we decided to exclude it from the results as we
found out that the nature of the task (participants had to watch body movements)
introduced an experimental bias: because dance is a form of whole-body
expression, gazes where evenly distributed on the body of the agents, masking
possible cognition-related gaze patterns.

@@

>>>>

\rightheader{Cognitive Priming: Impact on the Perception of a Robot}   % This should be the title, or a shortened version of the title if your title is long.
\leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
\title{Cognitive Priming: Impact on the Perception of a Robot}

@@

\keywords{human-robot interaction, anthropomorphism, cognitive priming, eye-tracking, gaze patterns}

@@

Robotics researchers often tend to consider that anthropomorphism only describes
a static set of human-like features of a robot (like its shape, its speech
capabilities, facial expressions, etc.).
Following~\citet{fink_anthropomorphism_2012}, we refer to these characteristics
as the \emph{anthropomorphic design} of the robot, and we call
\emph{anthropomorphism} the general \emph{social phenomenon} that emerges from
the (real or imagined) interaction between a non-human agent (a robot in our
case) and a human~\citep{persson_anthropomorphism_2000}.  According
to~\citet{epley_when_2008}, anthropomorphism includes the human perception of
emotional states, motivations, intentions in the non-human agent, and tends to
ascribe those qualities to it. As such, the dynamic and socio-cognitive
dimensions of anthropomorphism are essential to understand the complex bonds
that human users build with artificial agents such as
robots~\citep{lemaignan2014dynamics}. Therefore anthropomorphism appears to be a
useful \emph{proxy} to study these intricate psychological
bonds. Going in that direction, this article introduces a new way to assess
anthropomorphic attributions and provides in particular new insights on
the impact of \emph{cognitive priming} on anthropomorphic
attributions.

@@

We actually build several hypotheses: our baseline hypothesis \h{1} is that we
can actually create such stimuli that induce recognisable \emph{shallow} or
\emph{deeper} cognitive ascriptions onto the robot (manipulation check); and
further that these different levels of cognitive ascriptions are interpreted by
the participants as being respectively \emph{machine-like} (low level of
anthropomorphic attributions) or \emph{human-like} (higher level of
anthropomorphic attributions).

@@

Then, we hypothesize (\h{3}) that the gaze fixations on the head are
significantly different depending on the cognitive priming, and that a deeper
cognitive priming corresponds to longer gaze fixations on the head. This would
in turn interpreted at \emph{gaze fixations on the head is a proxy for the level
of human-likeness attribution}, and constitutes the core hypothesis of this
article.

Finally, the hypothesis \h{4} examines whether the cognitive priming affects the
general tendency to anthropomorphize, \ie whether observing \emph{one}
robot acting in an \emph{human-like} context leads to an increased level of
anthropomorphic attributions to robots \emph{in general}. This also provides us
with a way to triangulate the behavioural measures with the subjective
attribution of anthropomorphism: if such an effect is found, we can also
conclude that the cognitive priming impacts on the attribution of human-likeness,
and this, in turns, supports the hypothesis \h{3} that head fixations would
reflect not only the cognitive context of the interaction but also the level of
anthropomorphic attributions.

Figure~\ref{hyps} illustrate how these four hypotheses relate to \emph{a)}
cognitive priming, \emph{b)} anthropomorphic attributions, and \emph{c)} gaze
patterns.

@@

    \node at (0,0) (ctxt) {cognitive priming};
    \node at (-3,-3) (anthro) {Anthropomorphic attributions};
    \node at (3,-3)[circle split, text width=2.5cm] (gaze) {\textit{\small Fixations \\on head} \nodepart{lower} \textit{\small Gaze
distribution \\differences}};
    \node [draw=none,anchor=east,left=-0.5cm of gaze.west] (gazecap) {\large Gaze:};

@@

\section{Experimental Design}

This study is build as an eye-tracking experiment (using a stationary
eye-tracker SMI RED 250) where participants watch short videos of an agent --
either a robot (Aldebaran Robotics' Nao) or a human -- performing simple
task (picking an object or pointing toward a sound source) after being primed.
The priming is designed to elicit either shallow cognitive ascriptions onto the
robot (leading to a \emph{machine-like} situation) or deeper cognitive
ascriptions (leaning toward a \emph{human-like} situation).

@@

The study follows a 2$\times$2 design, summarized in table~\ref{table:design}.
Our two independent variables are the level of cognitive priming (\emph{shallow}
\vs \emph{deep}) and the nature of the agent appearing in the stimulus (a robot,
eliciting a \emph{human-robot} interaction situation, or a human, eliciting a
\emph{human-human} interaction situation).

@@

    \tikzmark{left}
    \begin{tabular}{l|p{4cm}|p{4cm}}
        & \tikzmark{top1} Shallow cognitive priming & Deep cognitive priming \tikzmark{top2}  \\
        \hline
        \tikzmark{left1} Robot & {\bf A}: \emph{``Pick the brown toy''} & {\bf A}: \emph{``Pick your favorite toy''} \\
                               & {\bf B}: \emph{``Point at the noise''} & {\bf B}: \emph{``Point at the crying baby''} \\
        \hline
        \tikzmark{left2} Human & {\bf A}: \emph{``Pick the brown toy''} & {\bf A}: \emph{``Pick your favorite toy''} \\ 
                               & {\bf B}: \emph{``Point at the noise''} & {\bf B}: \emph{``Point at the crying baby''}\tikzmark{bottom} \\
        \end{tabular}

@@

    \caption{\small The study follows a 2$\times$2 design: the \emph{robot} vs
        \emph{human} condition is within subject, while the \emph{shallow
        cognitive priming} \vs \emph{deep cognitive priming} is between subjects.
        Two stimuli (\emph{Picking} task, {\bf A}, and \emph{Pointing} task,
        {\bf B}) were shown to the participants, introduced by brief verbal
        commands, reproduced in the table. Figure~\ref{fig:stimuli} shows
        pictures of the four stimuli.}

@@

The audio (and audio only) of these four videos was then edited to create two
sets of stimuli: one for the \emph{shallow cognitive priming} condition, one for
the \emph{deep cognitive priming} condition. The audio editing consisted in
inserting different commands to initiate the tasks (reported in
table~\ref{table:design}): in the \emph{Picking} task for instance, the object
that the agent had to pick was described either as a \emph{``brown toy''} or as
\emph{``your favorite toy''}. In the former case, the object was refered through
visible, objective features which do not suppose as deep cognitive capabilities
as in the latter case where the agent is implicitly supposed to have
tastes and preferences such as it can choose a toy as its favorite.

This simple verbal priming (\emph{``brown toy''} \vs \emph{``your favorite
toy''}) set the expectations regarding the cognitive capabilities of the robot
(\emph{shallow} \vs \emph{deep}) and was expected to lead to different
perceptions of the interaction (\emph{machine-like} \vs \emph{human-like}). We
reinforced this effect in the \emph{Pointing} task: not only the verbal priming
but also the sound played by the speakers during the task was altered: either a
repetitive bip (\emph{shallow cognitive priming}) or the sound of a crying baby
(\emph{deeper cognitive priming}).

@@

\section{Method}

@@

As stated previously, the study follows a 2$\times$2 design
(table~\ref{table:design}): the \emph{shallow} \vs \emph{deep cognitive priming}
condition was between-subjects (30 participants performed the \emph{deep cognitive}
tasks while 26 were in the \emph{shallow cognitive} condition); the \emph{robot}
\vs \emph{human} condition was within-subject (the order of stimuli presentation
was counter-balanced over the participants). The study lasted in average 15
minutes per participant.

@@

\section{Results}

Based on the experiments conducted on 56 participants in the human and robot
interactions across \emph{shallow} and \emph{deep cognitive priming} conditions,
we have the following results.\footnote{The detailed statistics and code used
    for obtaining the results are available here :
\url{https://github.com/chili-epfl/anthropomorphism-eyetracking}.}

@@

Participants were asked in the post-questionnaire whether the video presented a
\emph{``robot kind of task''} or a \emph{``human kind of task''} on a 5-points
scale (numerical values ranging from -2 to 2, where -2 refers to robot kind of
task). As can be seen in figure 2, we got a significant correlation in this
manipulation check ($F(1,54) = 29.0, p < .001$) which validates our manipulation
and supports \h{1}: the participants that were shown the \emph{shallow cognitive
context} videos identified the task as more robot-like and participants watching
the videos with deeper cognitive priming perceived the tasks as more human-like.

@@

\subsection{Gaze Behaviours in Response to Shallow \vs Deep Cognitive Priming}

We consider the 5 groups of AOIs {\sf head}, {\sf arms}, {\sf hands}, {\sf
torso} and {\sf legs} (the left and right arms, hands and legs are grouped
together). Based on ANOVA results for the robot in both the shallow and deep
cognitive priming conditions, the fixations on the head in the deep condition
were found to be significantly higher than that in the shallow condition
($F(1,54) = 4.2, p < .05$\fixme{put the exact p value here}). For all other AOIs groups, the fixations across
shallow and deep conditions were almost the same. Figure~\ref{h3} shows the
distribution of proportion of time spent gazing on the 5 AOI groups for the two
conditions.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.6\columnwidth]{GazeHighLow}\label{GazeHighLow}
    \caption{Gaze fixations on the different areas on interest, for shallow \vs
    deep cognitive priming conditions.}
    \label{h3}
\end{figure}

@@

Note that we only analysed these possible correlations for robot condition: in
the human condition, the presence of the human is intrinsically a source of deep
cognitive expectations, hiding the effects of our manipulation on a shallow \vs deep
cognitive priming.

\subsection{Correlation Between Cognitive Priming and Changes in Anthropomorphic
Attributions}

Running an ANOVA against the change of anthropomorphic attributions
(\deltaant) over the duration of the experiment in the two cognitive
conditions, shows that \deltaant is greater for tasks with a deeper cognitive
context than that for the shallow cognitive tasks ($F(1,54) = 6.54, p <
.05$\fixme{put the exact p value here},
figure~\ref{h4}). In other words, after being exposed to short videos of a robot
performing simple tasks, participants primed with a deeper cognitive
expectations report a significantly higher tendency to anthropomorphize robots
\emph{in general} (as the questionnaire on anthropomorphic attributions
explicitly referred to \emph{robots in general}).

\begin{figure}
    \centering
    \includegraphics[width=3.3in]{H4}\label{ICAtoAAPImprovement}
    \caption{Difference between \anti{} and \antf{} in the shallow and deep
    cognitive priming conditions.}
    \label{h4}
\end{figure}

This result supports \h{4} and validate that the cognitive priming impacts the
attribution of anthropomorphic features to robots. This, in turn, supports the
\emph{proxy} hypothesis of \h{3}: \emph{head fixations are a proxy for higher
levels of human-likeness attributions}.

@@

\section{Discussion}

@@

The significant correlation between deep \vs shallow conditions and the
answers to the question \emph{Were the task more robot-like or human-like?}
shows that our manipulation was successful, and that a shallow cognitive
context was indeed associated to a robot-like situation, while a deeper
cognitive priming was associated to a human-like situation (\h{1}). This is
already an interesting result: subtle changes in the cognitive priming are
recognized and clearly interpreted in terms of human-likeness.

@@

The third hypothesis \h{3} proposes that head fixations are related to the
cognitive expectations, which is clearly supported by our data: after deeper cognitive
priming, one tends to spend more time looking at the head of the interacting
agent than after shallow cognitive priming. We also hypothesized that, in turn,
head fixations could act as a \emph{proxy to anthropomorphic projections}: as
underlined in the previous section, our data also support this.

Finally, the hypothesis \h{4} looks at the dynamic of anthropomorphic
projections, with the hypothesis that watching an interaction with a particular
robot after a deeper cognitive priming may impact \emph{globally} the
anthropomorphic perceptions of robots. This is supported by our study.

@@

Finally, the situations needed to support two possible kind of cognitive priming
(shallow \vs deeper cognitive priming), and triggering one or the other of these
contexts needed to be done \emph{without changing} the visual part of the
stimulus.

We initially prepared three different stimuli: the \emph{Picking} task, the
\emph{Pointing} task and a \emph{Dance} task.  During the \emph{Dance} task, the
agent was either asked to \emph{``Show some movements''} (\emph{shallow
cognitive priming} condition) or to \emph{``Dance with the music''}
(\emph{deeper cognitive priming} condition). While all the participants were
shown this stimuli as well, we decided to exclude it from the results as we
found out that the nature of the task (participants had to watch body movements)
introduced an experimental bias: because dance is a form of whole-body
expression, gazes where evenly distributed on the body of the agents, masking
possible cognition-related gaze patterns.

@@

\section{Conclusion}

The study and results presented in this article lead to two main contributions:
new insights on the impact of the cognitive priming on the perception of a robot
by humans; a novel unbiased methodology based on eye-tracking to assess
anthropomorphic attributions during a running human-robot interaction.

This leads to a second-order effect that we also evidence here: depending on the
cognitive priming, the tendency to attribute human-like characteristics to robot
evolves in significantly different ways. After observing a robot in a
context that pre-suppose deeper cognitive capabilities, people increase
their general tendency to anthropomorphize robots compared to a shallow
cognitive priming, even though the robot appearance and visual behaviour is the
exact same.

\fixme{Properly conclude the paper: what does our research reveals?}
